### 2015-07-07 narrative/data-reduction.tex
editing 1.3.2

In the case of C. S. Chang described earlier, in common with most other
applications scientists with whom we collaborate, information is provided on
which data should be sent over to our SSIO layer in order that the best
possible information is available for the subsequent analysis. The decision as
how this should be accomplished generally involves data refactoring
(re-organizing and reducing the data).

>>>>

In the case of C. S. Chang described earlier, and common with most other
applications scientists with whom we collaborate, information is provided on
which data should be sent over to the SSIO layer so that the best, and most
important information is available for subsequent analysis.
This is generally accomplished using refactoring, which includes re-organization and reductions of the data.
